### 2016-05-31 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Switched NF near and far data for Test 16 plot

Tests 6 and 7 followed identical procedures that involved using a 1.75~in handline equipped with a combination nozzle to flow water from the north side double doors of the Two Story Structure into the first floor room. The water stream was aimed at the south side wall of the first floor during the experiments. Test 6 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, and Test 7 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}. Each experiment began by using a straight stream to flow water in a fixed, horizontal position. After 60 seconds of water flow, the stairwell door was opened. One minute later, the west double door on the north side of the second floor was opened, and water continued to flow for 60 seconds. Next, the water flow was stopped, the two doors were closed, and the procedure was repeated three additional times for the sweeping (back and forth left-to-right), clockwise, and counterclockwise application patterns. This entire process was repeated using narrow fog and wide fog streams. Fig.~\ref{fig:test_6_pic} contains an image of a straight stream pattern being applied during Test 6 with the flow path fully established.

>>>>

Tests 6 and 7 followed identical procedures that involved using a 1.75~in handline equipped with a combination nozzle to flow water from the north side double doors of the Two Story Structure into the first floor room. The water stream was aimed at the south side wall of the first floor during the experiments. Test 6 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, and Test 7 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}. Each experiment began by using a straight stream to flow water in a fixed, horizontal position. After 60 seconds of water flow, the stairwell door was opened. One minute later, the west double door on the north side of the second floor was opened, and water continued to flow for 60 seconds. Next, the water flow was stopped, the two doors were closed, and the procedure was repeated three additional times for the sweeping (back and forth, left-to-right), clockwise, and counterclockwise application patterns. This entire process was repeated using narrow fog and wide fog streams. Fig.~\ref{fig:test_6_pic} contains an image of a straight stream pattern being applied during Test 6 with the flow path fully established.
